Case study validations of automatic bullet matching

### 2018-09-28 index.Rmd
change in rda

```{r signatures, fig.width = 10, fig.height = 4, fig.cap="Signatures of all six lands of bullets 1 and 2 from barrel 1 of the Hamby set 44."}
# signatures for one bullet
h44cc <- readRDS("data/h44-ccdata.rda")
br1 <- h44cc[1:12]
dframe <- 1:12 %>% purrr::map_df(.f = function(i) {
  d <- br1[[i]]
  d <- d %>% group_by(y) %>% summarize(
    value = mean(value, na.rm=TRUE)
  )
  d$id <- i
  d %>% ungroup(y) %>% rename(
    x = y
  )
})

dframe$bullet <- rep(c("Bullet 1", "Bullet 2"), each = 6)[dframe$id]
dframe$land <- paste("Land", (dframe$id %% 6 + 1))

dframe <- dframe %>% group_by(bullet, land) %>% nest()
names(dframe)[3] <- "ccdata"

library(bulletxtrctr)
dframe <- dframe %>% mutate(
  grooves = ccdata %>% 
    purrr::map(.f = cc_locate_grooves, method = "middle", 
               adjust = 30, return_plot = TRUE)
)
dframe <- dframe %>% mutate(
  sigs = purrr::map2(
    .x = ccdata, .y = grooves, 
    .f = function(x, y) {
      cc_get_signature(
        ccdata = x, grooves = y, span1 = 0.75, span2 = 0.03)
    })
)
dframe$barrelland <- dframe$land
idx <- which(dframe$bullet=="Bullet 2")
dframe$landid <- parse_number(dframe$land)
dframe$landid[idx] <- (dframe$landid[idx] +1) %% 6 + 1
dframe$land <- paste("Land", dframe$landid)

signatures <- dframe %>% select(bullet, land, sigs) %>% tidyr::unnest()
signatures %>% 
  ggplot(aes(x = x/1000)) + 
  geom_line(aes(y = raw_sig), colour = "grey70") +
  geom_line(aes(y = sig), colour = "grey30") +
  facet_grid(bullet~land) +
  ylim(c(-5,5)) +
  theme_bw() +
  ylab("Surface measurement (in microns)") +
  xlab("Relative Location (in millimeters)") 
```

>>>>

```{r signatures, fig.width = 10, fig.height = 4, fig.cap="Signatures of all six lands of bullets 1 and 2 from barrel 1 of the Hamby set 44."}
# signatures for one bullet
# h44cc <- readRDS("data/h44-ccdata.rda")
# br1 <- h44cc[1:12]
# dframe <- 1:12 %>% purrr::map_df(.f = function(i) {
#   d <- br1[[i]]
#   d <- d %>% group_by(y) %>% summarize(
#     value = mean(value, na.rm=TRUE)
#   )
#   d$id <- i
#   d %>% ungroup(y) %>% rename(
#     x = y
#   )
# })
# 
# dframe$bullet <- rep(c("Bullet 1", "Bullet 2"), each = 6)[dframe$id]
# dframe$land <- paste("Land", (dframe$id %% 6 + 1))
# 
# dframe <- dframe %>% group_by(bullet, land) %>% nest()
# names(dframe)[3] <- "ccdata"
# 
# library(bulletxtrctr)
# dframe <- dframe %>% mutate(
#   grooves = ccdata %>% 
#     purrr::map(.f = cc_locate_grooves, method = "middle", 
#                adjust = 30, return_plot = TRUE)
# )
# dframe <- dframe %>% mutate(
#   sigs = purrr::map2(
#     .x = ccdata, .y = grooves, 
#     .f = function(x, y) {
#       cc_get_signature(
#         ccdata = x, grooves = y, span1 = 0.75, span2 = 0.03)
#     })
# )
# dframe$barrelland <- dframe$land
# idx <- which(dframe$bullet=="Bullet 2")
# dframe$landid <- parse_number(dframe$land)
# dframe$landid[idx] <- (dframe$landid[idx] +1) %% 6 + 1
# dframe$land <- paste("Land", dframe$landid)

signatures <- read.csv("data/signatures.csv")
signatures <- dframe %>% select(bullet, land, sigs) %>% tidyr::unnest()
signatures %>% 
  ggplot(aes(x = x/1000)) + 
  geom_line(aes(y = raw_sig), colour = "grey70") +
  geom_line(aes(y = sig), colour = "grey30") +
  facet_grid(bullet~land) +
  ylim(c(-5,5)) +
  theme_bw() +
  ylab("Surface measurement (in microns)") +
  xlab("Relative Location (in millimeters)") 
```
